Sustainable computational science:\\ the ReScience initiative

### 2017-07-10 draft.tex

In theory, computation is a deterministic process and exact
reproduction should therefore be trivial. In reality, it is very
difficult to achieve because of the complexity of today's software
stacks and the tediousness of recording all interactions between a
scientist and a computer 
\citep[although a number of recent tools have attempted to automate such recording, e.g.][]{guo:2011, davison:2012, murta:2015}.
\citeauthor{Mesnard:2016} explain
\citep{Mesnard:2016} how difficult it can be to reproduce a two-year
old computation even though all possible precautions were taken at the
time to ensure reproducibility.  The most frequent obstacles are the
loss of parts of the software or input data, lack of a computing
environment that is sufficiently similar to the one used initially,
and insufficient instructions for making the software work. An
obstacle specific to numerical computations is the use of
floating-point arithmetic, whose rules are subject to slightly
different interpretations by different compilers and runtime support
systems. A large variety of research practices and support tools have
been developed recently to facilitate reproducible computations. For a
collection of recipes that have proven useful, see
\citet{kitzes:2017}.

>>>>

In theory, computation is a deterministic process and exact
reproduction should therefore be trivial. In reality, it is very
difficult to achieve because of the complexity of today's software
stacks and the tediousness of recording all interactions between a
scientist and a computer.  \citeauthor{Mesnard:2016} explain 
\citep{Mesnard:2016} how difficult it can be to reproduce a two-year
old computation even though all possible precautions were taken at the
time to ensure reproducibility.  The most frequent obstacles are the
loss of parts of the software or input data, lack of a computing
environment that is sufficiently similar to the one used initially,
and insufficient instructions for making the software work. An
obstacle specific to numerical computations is the use of
floating-point arithmetic, whose rules are subject to slightly
different interpretations by different compilers and runtime support
systems. A large variety of research practices and support tools have
been developed recently to facilitate reproducible computations. For a
collection of recipes that have proven useful, see
\citet{kitzes:2017}.
